Organisational Environment

Draig Technology is a small software company located in Bangor north Wales, it was founded in 1999, by Richard Sheppard who is the managing director.  Since then it has worked on a variety of different projects ranging from web design, Microsoft Share Point, network management and other bespoke software packages.   For the last few years Draig has specialised in being the leading supplier in the UK for CRM (Customer Relationship Management) and Billing solution in the energy sector for small to medium sized companies. Draig is a Microsoft certified business and has been financially stable for over 10 years. 

The company is split into two teams. The first is the support team, which provides support for DBS (Draig Billing System).  This consists of triaging client issues, testing new versions of DBS and coordinating with clients when an update or patch is to be applied. The second team is development, which mainly works on DBS, as well as providing support for any data clean ups or major bug fixes.

I was employed in the support team, as technical support. When I started there were three teams, Support, Testing and Development. During that time I worked mainly with testing and support, my main duty was to support. After about seven months the leader of the testing team left the company, and the testing and support were merged into one.  

[ Diagram of Teams before and after ]

Each team has a line manager, which reports to the managing director. We also have separate client managers which are in charge of one or more clients, they communicate with team managers to insure that their client's interest is being looked after.

Two months before I left, I was put in charge of training a new employee for the support team.


Technical and Application Environments

Draig have around three main servers. All the servers are Dell Power edge, with the main server having 16GB RAM 2TB HDD and Intel Dual Core Xeon. The workstations are split up into two types, development and management. Development machines consists of a Dell XPS, with an Intel Quad Core, 8GB RAM and 1TB HDD. Management machines varied from mid range desktops to laptops, the majority was laptops with 4GB RAM and 500GB HDD. All machines have dual monitors, of good quality.

Draig is a Microsoft based company, which means that all of the software and services are Microsoft based. Draig have a main domain server which is used for VPN and user administration. The email service is outsourced to a company called simply mail solutions, which provides web access and Microsoft Exchange. All of the workstations are configured to use outlook 2007/12 and the exchange server. Development is done using Visual Studio 2007/12. For code management and client support, e.g. reporting software issues, we use Team Foundation Server (TFS) which is an extension  to Visual Studio. TFS provides clients with a web interface to report and track issues, and developers with version control.

